---
title       : Unemployment in Europe Explorer
subtitle    : Developing Data Products Course Project
author      : Alfredo Parreño
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: libraries/nvd3}
---

## Dataset

The aplication is based on the data collected by [Eurostat](http://ec.europa.eu/eurostat).
The indicator focuses on the 15 to 74 years old.

The indicator provides a measure of difficulties that people with different levels of education have to face in the labour market and offers a first idea of the impact of education in reducing the chances of being unemployed.

The dataset has been obtained from [link](http://ec.europa.eu/eurostat/web/lfs/data/main-tables#).

--- 

## Education and gender

```{r , comment = NA, message = F, echo = F}
library(dplyr)
library(data.table)
data <- read.csv("lfsa_urgaed_1_Data.csv")
data <- data[, -c(4,6,8)]
data$Value <- as.numeric(gsub("[^0-9|.]","",as.character(data$Value)))
```

The education has been divided in the following levels

```{r}
levels(data$ISCED11)
```

While gender is divided in:

```{r}
levels(data$SEX)
```

---

## What can you do?

- You can compare the unemployment rates in the european countries by ploting the rates from 2003 to 2014.
There are unemployment data of `r length(levels(data$GEO))` countries and agrupation of countries.
- You can filter data by sex.
- You can filter data by education.

---

## Interactive graphics
You will get an interactive graphic with the information selected.

```{r 'Figure1', results = 'asis', comment = NA, message = F, echo = F}
    require(rCharts)
    data$TIME <- as.character(data$TIME)
    dataFiltered <- data %>% filter(GEO %in% c("European Union (28 countries)", "Spain", "Italy", "France", "Ireland"), SEX=="Total", ISCED11=="All ISCED 2011 levels ") %>%
        group_by(GEO)
    m1 <- nPlot(Value~TIME, type = "lineChart", group = "GEO", data = dataFiltered)
    m1$chart(margin = list(left = 100))
    m1$yAxis( axisLabel = "Unemployment Rate (%)", width = 50)
    m1$xAxis( axisLabel = "Year", width = 70)
    m1$save('Figure1.html', standalone = TRUE)
```
<iframe src ='Figure1.html', width = "860px", height = "450px"></iframe>

